### 2023-03-10 dev/_intro.qmd
build based on f58d905

data_train, data_test = Data.train_test_split(counterfactual_data)
Models.train(mod, data_train; n_epochs=n_epochs)
plt_original = plot(mod, counterfactual_data; zoom=0, colorbar=false)
display(plt_original)
```

>>>>

data_train, data_test = Data.train_test_split(counterfactual_data)
CounterfactualExplanations.Models.train(mod, data_train; n_epochs=n_epochs)
plt_original = plot(mod, counterfactual_data; zoom=0, colorbar=false)
display(plt_original)
```
